---
title: "Portfolio 6"
author: "AwesomePie1453"
date: "3/12/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Introduction

For my 6th portfolio, I will be using R code to put together a couple graphs for my pokemon guild I am a part of, Spear Pillar. This guild has three houses, one of which, the Midnight Reapers, I am the captain of. We decided to do an inner-house tournament. Each participant (there were 12 of us) put together a team of 6 mons using standard Spear Pillar rules, but with 18 extra banned pokemon that are overused. The following data (reapers.sav) provides the kills and deaths of each pokemon used by each trainer, in addition to their item. I will be using this space to put together some charts for my guild to see
```{r read, include=FALSE}
library(haven)
library(tidyverse)
library(gridExtra)
library(ggrepel)
Reapers<-read_sav("Reapers.sav")

```

First, here are the Kills and Deaths for each trainer

```{r Names}
Pie <- Reapers %>%
  filter(Trainer == "Pie")
Alex <- Reapers %>%
  filter(Trainer == "Alex")
Flygon <- Reapers %>%
  filter(Trainer == "Flygon")
Beast <- Reapers %>%
  filter(Trainer== "Beast")
Nuno <- Reapers %>%
  filter(Trainer == "Nuno")
Daizook <- Reapers %>%
  filter(Trainer == "Daizook")
Chrispy <- Reapers %>%
  filter(Trainer == "Chrispy")
MVF <- Reapers %>%
  filter(Trainer == "MVF")
Trees <- Reapers %>%
  filter(Trainer == "Trees")
Seddy <- Reapers %>%
  filter(Trainer == "Seddy")
Jay <- Reapers %>%
  filter(Trainer == "Jay")
```


```{r}
attach(Pie)
PieGraph <- ggplot(data=Pie,aes(x=Deaths,y=Kills,label=Pokemon)) + 
  geom_point(aes(color=Pokemon)) +
  geom_text(vjust=1.4, size=3.5) + scale_x_reverse(lim=c(8,5)) + labs(title="Pie's Pokemon KD") + theme(legend.position="none", plot.title=element_text(hjust=.5))

attach(Flygon)
FlygonGraph <- ggplot(data=Flygon,aes(x=Deaths,y=Kills,label=Pokemon)) + 
  geom_point(aes(color=Pokemon)) +
  geom_text(vjust=1.4, size=3.5) + scale_x_reverse(lim=c(12,0)) + labs(title="Flygon's Pokemon KD") + theme(legend.position="none", plot.title=element_text(hjust=.5))

attach(Alex)
AlexGraph <- ggplot(data=Alex,aes(x=Deaths,y=Kills,label=Pokemon)) + 
  geom_point(aes(color=Pokemon)) +
  geom_text(vjust=1.4, size=3.5) + scale_x_reverse(lim=c(12,0)) + labs(title="Alex's Pokemon KD") + theme(legend.position="none", plot.title=element_text(hjust=.5))

attach(Chrispy)
ChrispyGraph <- ggplot(data=Chrispy,aes(x=Deaths,y=Kills,label=Pokemon)) + 
  geom_point(aes(color=Pokemon)) +
  geom_text(vjust=1.4, size=3.5) + scale_x_reverse(lim=c(12,0)) + labs(title="Chrispy's Pokemon KD") + theme(legend.position="none", plot.title=element_text(hjust=.5))

attach(Nuno)
NunoGraph <- ggplot(data=Nuno,aes(x=Deaths,y=Kills,label=Pokemon)) + 
  geom_point(aes(color=Pokemon)) +
  geom_text(vjust=1.4, size=3.5) + scale_x_reverse(lim=c(12,0)) + labs(title="Nuno's Pokemon KD") + theme(legend.position="none", plot.title=element_text(hjust=.5))

attach(Trees)
TreesGraph <- ggplot(data=Trees,aes(x=Deaths,y=Kills,label=Pokemon)) + 
  geom_point(aes(color=Pokemon)) +
  geom_text(vjust=1.4, size=3.5) + scale_x_reverse(lim=c(12,0)) + labs(title="Tree's Pokemon KD") + theme(legend.position="none", plot.title=element_text(hjust=.5))

attach(Beast)
BeastGraph <- ggplot(data=Beast,aes(x=Deaths,y=Kills,label=Pokemon)) + 
  geom_point(aes(color=Pokemon)) +
  geom_text(vjust=1.4, size=3.5) + scale_x_reverse(lim=c(12,0)) + labs(title="Beast's Pokemon KD") + theme(legend.position="none", plot.title=element_text(hjust=.5))

attach(MVF)
MVFGraph <- ggplot(data=MVF,aes(x=Deaths,y=Kills,label=Pokemon)) + 
  geom_point(aes(color=Pokemon)) +
  geom_text(vjust=1.4, size=3.5) + scale_x_reverse(lim=c(12,0)) + labs(title="MVF's Pokemon KD") + theme(legend.position="none", plot.title=element_text(hjust=.5))

attach(Daizook)
DaizookGraph <- ggplot(data=Daizook,aes(x=Deaths,y=Kills,label=Pokemon)) + 
  geom_point(aes(color=Pokemon)) +
  geom_text(vjust=1.4, size=3.5) + scale_x_reverse(lim=c(12,0)) + labs(title="Daizook's Pokemon KD") + theme(legend.position="none", plot.title=element_text(hjust=.5))

attach(Seddy)
SeddyGraph <- ggplot(data=Seddy,aes(x=Deaths,y=Kills,label=Pokemon)) + 
  geom_point(aes(color=Pokemon)) +
  geom_text(vjust=1.4, size=3.5) + scale_x_reverse(lim=c(12,0)) + labs(title="Seddy's Pokemon KD") + theme(legend.position="none", plot.title=element_text(hjust=.5))

attach(Jay)
JayGraph <- ggplot(data=Jay,aes(x=Deaths,y=Kills,label=Pokemon)) + 
  geom_point(aes(color=Pokemon)) +
  geom_text(vjust=1.4, size=3.5) + scale_x_reverse(lim=c(12,0)) + labs(title="Jay's Pokemon KD") + theme(legend.position="none", plot.title=element_text(hjust=.5))

```



```{r Graphs}
grid.arrange(PieGraph, FlygonGraph, NunoGraph, JayGraph, AlexGraph, BeastGraph, TreesGraph, SeddyGraph, MVFGraph, ChrispyGraph, DaizookGraph, ncol=2)
```
Here are the KDs for everyone graphed


```{r everyone}
ggplot(data=Reapers,aes(x=Deaths,y=Kills,label=Pokemon)) + 
  geom_point(aes(color=Pokemon)) +
  geom_text(vjust=1.4, size=3.5) + scale_x_reverse(lim=c(12,0)) + labs(title="Reaper League's Pokemon KD") + theme(legend.position="none", plot.title=element_text(hjust=.5))
```
Here is the display of items

```{r items}
Reapers %>%
ggplot(mapping = aes(x=Item)) + 
  geom_bar(aes()) + coord_flip()
```

Here is the display of Pokemon

```{r pokemon}
Reapers %>%
ggplot(mapping = aes(x=Pokemon)) + 
  geom_bar(aes()) + coord_flip()
```
If you combine each Pokemon to see overall who was the best, it would be shown on a combined graph with Lucario. 

```{r combined}
Reapers %>%
ggplot(mapping = aes(x=Pokemon, y=Kills, color=Deaths)) + 
  geom_col() + coord_flip()  
```

These are the results of the Reaper Tournament!